The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/main.tex

\newcommand\myworries[1]{\textcolor{red}{#1}}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{castle.png}
  \caption{tmp}
  \Description{}
  \label{fig:teaser}
\end{teaserfigure}

\begin{abstract}
We introduce a new method for direct physics-based animation of volumetric curved models.  
The Shape Matching Element Method is a completely meshless approach which is robust to gaps and overlaps in geometry, 
is compatible with standard constitutive models and time  integration schemes, supports contact and frictional interactions 
as well as direct editing of simulation output. 
We demonstrate the efficacy of our algorithm by producing compelling physics-based animations from a variety of curved input models.
\end{abstract}

>>>>

\acmSubmissionID{230}
\newcommand\myworries[1]{\textcolor{red}{#1}}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{figures/teaser_castle.pdf}
  \caption{Using the shape matching element method we can directly simulate this NURBS surface model of a bouncy castle as a volumetric elastic object without the need for volumetric meshing of any kind.}
  \label{fig:teaser}
\end{teaserfigure}

\begin{abstract}
We introduce a new method for direct physics-based animation of volumetric curved models, represented using NURBS surfaces.  
Our technical contribution is the Shape Matching Element Method (SEM).
SEM is a completely meshless algorithm, the first to simultaneously 
be robust to gaps and overlaps in geometry, 
be compatible with standard constitutive models and time integration schemes, support contact and frictional interactions  
and to preserve feature correspondence during simulation which enables editable simulated output. 
We demonstrate the efficacy of our algorithm by producing compelling physics-based animations from a variety of curved input models.
\end{abstract}
